Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 egpaper_final.tex
3.2 first pass, numbers still needed

To whiten a signal $x$, we have to solve $\Sigma w = x - \mu$ which takes $O(n^3)$ time. In \cite{Hariharan12}, the authors make use of the fact that covariance matrices are Hermitian and positive semidefinite to solve the system via the Cholesky decomposition, which is twice as fast as the LU decomposition. However, by considering the properties of the covariance matrix of the HOG template, we show that the conjugate gradient method can further speed up the whitening stage.

@@

Figure \ref{fig:spectral} shows the singular values of a template covariance matrix with a small regularization constant added to the diagonal. The singular values are clustered in small region and most of the energies are concentrated on the first \scream{x} singular values. Therefore, conjugate gradient will converge in $O(n^2\kappa)$ time, faster

We also used iterative Conjugate Gradient to make use of low rank property of the covariance \cite{Gharbi12}. After adding small regularization, the regularized covariance matrix has nice spectral property (Figure \ref{fig:spectral}). The singular values are clustered in small region and most of the energies are concentrated on the first (number) singular values. Thus, the conjugate gradients stage doesn't go upto the size of the matrix to converge.

@@

\begin{table*}[!htbp]
    \begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Methods &  without Calibration (AP/AVP) & time & w/ Calibration \cite{Aubry14} (AP/AVP) & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.28/48.38  &  31ms  & 60.37/50.19               &   8.7 sec \\ 
WHO-Chol\cite{Hariharan12} &              &3811ms    &                           &   12.4 sec  \\
WHO-GG                & 81.70/74.20  &104ms &     83.714/75.37              &   8.3 sec \\
WHO-CG-Z              & 54.42/49.71  &103ms & \textbf{92.80}/\textbf{81.44} &   8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG        & \textbf{90.00}/78.23 & 79ms & 90.31/78.00                   &  8.5 sec   \\
\hline
\end{tabular}
\end{center}
\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) \cite{Xiang14} of variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO\cite{Hariharan12} whitens all cell, WHO-ZZ whitens all cell then zero out textureless region. NZC-WHO-ZZ first substract mean $\mu$ on non-zero cells and whiten all cells then zero out textureless region. NZ-WHO whitens only non-zero cell. Note that WHO-ZZ got dramatic performance boost after calibration due to strong impact of substracting $\mu$ from all textureless region}
\label{tab:who_initializations}
\end{table*}

>>>>

To whiten a signal $x$, we have to solve $\Sigma w = x - \mu$. In \cite{Hariharan12}, the authors make use of the fact that covariance matrices are Hermitian and positive semidefinite to solve the system via the Cholesky decomposition, which is twice as fast as the LU decomposition. These decompositions require $O(n^3)$ time, whereas the conjugate gradient method takes $O(n^2\kappa)$ time, where $\kappa$ is the condition number of the matrix. This makes conjugate gradient a faster option for matrices with small condition numbers relative to their size.

Figure \ref{fig:spectral} shows the singular values of a covariance matrix for one HOG template after a small regularization constant is added to the diagonal. The condition number of of the matrix is \scream{x}, much smaller than the size of the matrix (7500). As a result, conjugate gradient converges in \scream{x ms}, two orders of magnitude faster than the system can be solved using the Cholesky factorization (\scream{5 s}).

@@

%We also used iterative Conjugate Gradient to make use of low rank property of the covariance \cite{Gharbi12}. After adding small regularization, the regularized covariance matrix has nice spectral property (Figure \ref{fig:spectral}). The singular values are clustered in small region and most of the energies are concentrated on the first (number) singular values. Thus, the conjugate gradients stage doesn't go upto the size of the matrix to converge.

@@

\begin{table*}[!htbp]
    \begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Methods &  without Calibration (AP/AVP) & time & w/ Calibration \cite{Aubry14} (AP/AVP) & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.28/48.38  &  31ms  & 60.37/50.19               &   8.7 sec \\ 
WHO-Chol\cite{Hariharan12} &              &3811ms    &                           &   12.4 sec  \\
WHO-CG                & 81.70/74.20  &104ms &     83.714/75.37              &   8.3 sec \\
WHO-CG-Z              & 54.42/49.71  &103ms & \textbf{92.80}/\textbf{81.44} &   8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG        & \textbf{90.00}/78.23 & 79ms & 90.31/78.00                   &  8.5 sec   \\
\hline
\end{tabular}
\end{center}
\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) \cite{Xiang14} of variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO\cite{Hariharan12} whitens all cell, WHO-ZZ whitens all cell then zero out textureless region. NZC-WHO-ZZ first substract mean $\mu$ on non-zero cells and whiten all cells then zero out textureless region. NZ-WHO whitens only non-zero cell. Note that WHO-ZZ got dramatic performance boost after calibration due to strong impact of substracting $\mu$ from all textureless region}
\label{tab:who_initializations}
\end{table*}
